Empirical Evaluation of eval in R

### 2020-12-15 analysis/Attic/counts.Rmd
changes

```{r callsite-distribution, eval=TRUE}
eval_callsite_table <-
  package_calls %>%
  mutate(
    site_count=cut(
      site_count, 
      breaks=c(0:10, 50, 100, 150, 200, 250, 300, Inf), 
      labels=c(1:10, "11--50", "51--100", "101--150", "151--200", "201--250", "251--300", "> 300"),
      include.lowest = T
    )
  ) %>%
  group_by(site_count) %>%
  summarize(package_count = n())

>>>>

```{r callsite-distribution, eval=TRUE}
package_evals_dynamic <- read_fst(PACKAGE_EVALS_DYNAMIC_FILE) %>% as_tibble()
eval_callsite_table <-
  package_evals_dynamic %>%
  mutate(
    site_count=cut(
      n, 
      breaks=c(0:10, 50, 100, 150, 200, 250, 300, Inf), 
      labels=c(1:10, "11--50", "51--100", "101--150", "151--200", "201--250", "251--300", "> 300"),
      include.lowest = T
    )
  ) %>%
  group_by(site_count) %>%
  summarize(package_count = n())
